\resumeSubheading
{Sales Associate}{Jun 2023 - Aug 2023}
{UNIQLO}{Orlando, FL}
\resumeItemListStart
  \resumeItem{Managed the sales floor by regulating stock, providing customer service, and communicating with staff.}
  \resumeItem{Provided technical support by troubleshooting software/hardware issues on point of sales systems, as well as self-checkout technology that emerged when the store upgraded to advanced RFID scanners.}
  \resumeItem{Worked on troubleshooting technology that assisted with the management of stock and staff communication.}
  \resumeItem{Worked with RFID technology in product tags, ensuring that technology was properly functioning.}
  \resumeItem{Tested security in RFID technology, ensuring that all security measures implemented were properly functioning.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{\href{https://github.com/must108/weather-app-1}{Weather App}} $|$ \emph{HTML, SCSS, JavaScript}}{June 2021 -- Present}
\resumeItemListStart
\resumeItem{Developed a web app that allows the user to search for the weather by city, and displayed weather information.}
\resumeItem{Utilized the OpenWeather API to access weather data such as temperature, a short description and related icons.}
\resumeItem{Seamlessly animated several UI components with SCSS and JavaScript to create an attractive UI.}
\resumeItem{Integrated asynchronous programming to efficiently access weather data from the API and handle potential errors.}
\resumeItemListEnd
ext experience just in case

\resumeProjectHeading
{\textbf{\href{https://github.com/must108/musicnotes}{Music Notes}} $|$ \emph{Python, GitHub Actions}}{June 2021 -- Present}
\resumeItemListStart
\resumeItem{Developed a Python library that allows developers to play piano/guitar music notes in their Python programs.}
\resumeItem{Hosted on the online repository PyPi, which allows for instant download with pip, Python's package manager.}
\resumeItem{Used GitHub Actions for CI/CD, allowing for automated unit testing, building, release, and deployment to pip.}
\resumeItem{Handled pull requests/issues from open-source contributors, and wrote clear documentation for users.}
\resumeItemListEnd

\resumeSubheading
{Information Technology Intern}{Jun 2022 - May 2023}
{Orange County Public Schools}{Orlando, FL}
\resumeItemListStart
  \resumeItem{Worked on resolving software and hardware issues on 2000+ Windows/MacOS computer systems and parts.}
  \resumeItem{Provided technical support for operating system software for 100+ staff members and 2500+ students.}
  \resumeItem{Resolved software/hardware issues for 100+ servers by troubleshooting software and repairing hardware.}
  \resumeItem{Collected information on an inventory of 3000+ devices in Microsoft Excel, and analyzed data to improve technical support performance.}
\resumeItemListEnd

\resumeSubheading
{Software Developer}{Jan 2024 - May 2024}
{Association of Computing Machinery}{Orlando, FL}
\resumeItemListStart
  \resumeItem{Collaborated with a team of designers and back-end engineers to develop a site advertising the ACM at UCF.}
  \resumeItem{Developed an admin tool that allows authorized users to manipulate server data directly from the website.}
  \resumeItem{Developed a REST API with Node.js and Express to route data from a MongoDB server to the front-end.}
  \resumeItem{Optimized a database querying algorithm, which reduced data fetching and component rendering runtime by 50\%.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{\href{https://github.com/must108/stock-model}{Stock Prediction Model}} $|$ \emph{Python, Jupyter Notebook, Pandas}}{June 2021 -- Present}
\resumeItemListStart
\resumeItem{Built a machine learning model that predicts the rise and fall of the S\&P500 Index price with historical data.}
\resumeItem{Utilized the Random Forest Classifier algorithm to train the model based on data imported from Yahoo Finance.}
\resumeItem{Manipulated and cleaned data by utilizing Pandas data frames and methods to ensure more accurate results.}
\resumeItem{Wrote the model in Jupyter Notebook, which allowed for better data visualization and more accurate predictions.}
\resumeItemListEnd