\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{soul}
\usepackage{setspace}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% \usepackage{lmodern}
% \usepackage{concmath}
 \renewcommand{\seriesdefault}{m}
\usepackage{lmodern}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Mustaeen Ahmed} \\ \vspace{1pt}
    \href{https://mustaeen.dev}{\ul{mustaeen.dev}} $|$ 
    \href{mailto:contact@mustaeen.dev}{\ul{contact@mustaeen.dev}} $|$ 
    \href{https://linkedin.com/in/mustaeenahmed}{\ul{linkedin.com/in/mustaeenahmed}} $|$
    \href{https://github.com/must108}{\ul{github.com/must108}} 
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Central Florida}{Orlando, FL}
      {Bachelor of Science in Computer Science}{Aug 2023 - May 2027}
      
  \resumeSubHeadingListEnd

  %-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: HTML, CSS, JavaScript, TypeScript, C, C++, Go, Java, Python, R, SQL} \\
     \textbf{Frameworks}{: React, Next.js, Astro, Node.js, Express.js, Tailwind CSS, tRPC, Bootstrap} \\
     \textbf{Libraries}{: scikit-learn, PyTorch, NumPy, Pandas, Matplotlib, Flask, Django, OpenCV} \\
     \textbf{Tools}{: Git, GitHub, MySQL, PostgreSQL, AWS, Prisma, Redis, Docker, MongoDB, Jupyter Notebook, Figma} \\
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{June 2024 - Present}
      {Darden}{Orlando, FL}
      \resumeItemListStart
        \resumeItem{Pioneered the development of several advanced Python applications for use in expediting and automating employee workflows, saving 400+ employee work hours per quarter and reducing quarterly employment costs by \$10000+.}
        \resumeItem{Leveraged several machine learning powered packages such as OpenCV, scikit-image, and PyTesseract for use in robust error handling, decreasing errors by 95\%, and increasing application efficiency by 45\%.}
        \resumeItem{Utilized packages such as Pandas, NumPy, and Matplotlib to perform efficient data engineering and develop concise data models, reducing application complexity by 50\%, and application runtime by 20\%.}
        \resumeItem{Developed a Java desktop application to streamline the use of our Python applications, improving employee user experience, software portability, and software maintainability by 100\%.}
        \resumeItem{Wrote a continuous integration tool with YAML to perform linting/formatting tasks on push, and wrote extensive documentation.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{Jan 2024 - May 2024}
      {Association of Computing Machinery}{Orlando, FL}
      \resumeItemListStart
        \resumeItem{Collaborated with a team of designers and back-end engineers to develop a site advertising the ACM at UCF.}
        \resumeItem{Developed an admin tool that allows authorized users to manipulate server data directly from the website.}
        \resumeItem{Developed a REST API with Node.js and Express to route data from a MongoDB server to the front-end.}
        \resumeItem{Optimized a database querying algorithm, which reduced data fetching and component rendering runtime by 50\%.}
      \resumeItemListEnd
     
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/naavis-app/app}{Naavis}} $|$ \emph{Next.js, React, TypeScript, PostgreSQL, Prisma, Redis, Amazon S3, tRPC, Tailwind CSS, Vitest}}{June 2021 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a location sharing web application which allows users to track locations of group members and devices.}
            \resumeItem{Wrote an advanced authentication system with TypeScript and Lucia, allowing for third-party and regular sign-in.}
            \resumeItem{Leveraged Amazon S3 and tRPC queries to store profile pictures and images for efficient retrieval of said assets.}
            \resumeItem{Used TypeScript and React to create appealing UI components and ensure responsive design throughout.}
          \resumeItemListEnd
                  
      \resumeProjectHeading
          {\textbf{\href{https://github.com/must108/multi-wordle}{Multi-Wordle}} $|$ \emph{Next.js, React, TypeScript, PostgreSQL, Prisma, Supabase, Node.js, Tailwind CSS, Vitest}}{June 2021 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a rendition of the popular game Wordle, with the addition of four and six letter game modes.}
            \resumeItem{Used React components, hooks, and props to seamlessly animate elements and develop core game functionality.}
            \resumeItem{Leveraged Node.js and Prisma to query a PostgreSQL database hosted on Supabase to access 10000+ words.}
            \resumeItem{Wrote unit tests in Vitest, allowing for testing of UI components, Prisma queries, and TypeScript events.}
          \resumeItemListEnd

        \resumeProjectHeading
            {\textbf{\href{https://github.com/must108/stock-model}{Stock Prediction Model}} $|$ \emph{Python, Jupyter Notebook, Pandas}}{June 2021 -- Present}
          \resumeItemListStart
            \resumeItem{Built a machine learning model that predicts the rise and fall of the S\&P500 Index price with historical data.}
            \resumeItem{Utilized the Random Forest Classifier algorithm to train the model based on data imported from Yahoo Finance.}
            \resumeItem{Manipulated and cleaned data by utilizing Pandas data frames and methods to ensure more accurate results.}
            \resumeItem{Wrote the model in Jupyter Notebook, which allowed for better data visualization and more accurate predictions.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{\href{https://github.com/must108/naturalization-test}{Naturalization Test App}} $|$ \emph{TypeScript, MySQL, Node.js, Express.js, Supabase, SCSS}}{June 2021 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a quiz app that simulates the civics test given during the U.S. citizen naturalization process.}
            \resumeItem{Queried a MySQL database hosted on Supabase with Node.js and Express to access 100+ questions and answers.}
            \resumeItem{Used TypeScript and SCSS to seamlessly animate website components and build an attractive UI.}
            \resumeItem{Tested on a small group of individuals studying for the real civics test; all users from the group passed the exam.}

          \resumeItemListEnd
    \resumeSubHeadingListEnd


%

%-------------------------------------------
\end{document}
