\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{soul}
\usepackage{setspace}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% \usepackage{lmodern}
% \usepackage{concmath}
 \renewcommand{\seriesdefault}{m}
\usepackage{lmodern}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\vspace*{-0.65in} % Adjust this value as needed
\begin{center}
    \textbf{\scshape Mustaeen Ahmed} \\ \vspace{1pt}
    \href{https://mustaeen.dev}{\ul{mustaeen.dev}} $|$ 
    \href{mailto:contact@mustaeen.dev}{\ul{contact@mustaeen.dev}} $|$ 
    \href{https://linkedin.com/in/mustaeenahmed}{\ul{linkedin.com/in/mustaeenahmed}} $|$
    \href{https://github.com/must108}{\ul{github.com/must108}} 
\end{center}


%-----------EDUCATION-----------
\vspace*{-0.24in} % Adjust this value as needed
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Central Florida}{Orlando, FL}
      {Bachelor of Science in Computer Science}{Aug 2023 - May 2027}
      
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer Intern}{June 2025 - Present}
      {Morgan Stanley}{New York, NY}
      \resumeItemListStart
          \resumeItem{\textbf{2nd place winner} of the "Best Overall" category at Knight Hacks 2024, surpassing \textbf{102} submitted projects.}
          \resumeItem{Developed a highly-interactive, educational mixed reality application for learning and practicing the guitar.}
          \resumeItem{Designed an \textbf{audio classification} algorithm which converts audio frequencies to binary data for note validation.}
          \resumeItem{Leveraged \textbf{C\#} to develop songs/lessons and core application logic, and utilized \textbf{Unity} for 3D development.}
    \resumeItemListEnd
    \resumeSubheading
      {Software Engineer Intern}{March 2025 - Present}
      {Ideaflow}{Palo Alto, CA}
      \resumeItemListStart
          \resumeItem{\textbf{2nd place winner} of the "Best Overall" category at Knight Hacks 2024, surpassing \textbf{102} submitted projects.}
          \resumeItem{Developed a highly-interactive, educational mixed reality application for learning and practicing the guitar.}
          \resumeItem{Designed an \textbf{audio classification} algorithm which converts audio frequencies to binary data for note validation.}
          \resumeItem{Leveraged \textbf{C\#} to develop songs/lessons and core application logic, and utilized \textbf{Unity} for 3D development.}    \resumeItemListEnd
    \resumeSubheading
      {Software Engineer Intern}{January 2025 - March 2025}
      {U.S. Department of Transportation}{Washington, D.C.}
      \resumeItemListStart
        \resumeItem{Developed and deployed a scalable web application with \textbf{AWS CDK (Cloud Dev. Kit)} and \textbf{TypeScript}.}
        \resumeItem{Reduced backend response time by \textbf{54\%} by leveraging \textbf{RESTful APIs} with \textbf{Amazon API Gateway}.} 
        \resumeItem{Improved communications efficiency by crafting solutions to handle \textbf{B2B Data Interchange} with \textbf{Amazon S3}.}
        \resumeItem{Implemented secure user authentication with \textbf{Amazon Cognito}, improving application security by \textbf{99\%}.}
        \resumeItem{Developed a vessel tracking interface with \textbf{AWS Lambda} and \textbf{DynamoDB}, improving port scheduling operations by \textbf{28\%}, and port throughput by \textbf{44\%}.}
    \resumeItemListEnd
      \resumeSubheading
      {Software Engineer Intern}{September 2024 - May 2025}
      {Leidos}{Orlando, FL}
      \resumeItemListStart
        \resumeItem{Researched solutions for advancing the field of \textbf{spatial intelligence}, focusing on generating complex relationships between visual data and language by leveraging \textbf{LLMs}, \textbf{Q-Formers}, and \textbf{Hugging Face Transformers}.}
        \resumeItem{Fine-tuned \textbf{machine learning} models for \textbf{vision-language pre-training}, increasing model efficiency by \textbf{37\%}.}
        \resumeItem{Constructed \textbf{data scraping} tools with \textbf{Python}, automating data collection and increasing productivity by \textbf{20\%}.}
        \resumeItem{Manipulated data through cleaning and preparation for efficient model training, reducing data errors by \textbf{15\%}. }
    \resumeItemListEnd
    \resumeSubheading
      {Software Engineer Intern}{June 2024 - November 2024}
      {Darden}{Orlando, FL}
      \resumeItemListStart
        \resumeItem{Engineered several \textbf{Python} applications for automation, saving \textbf{400+} work hours and \textbf{\$10000+} per quarter.}
        \resumeItem{Leveraged several \textbf{machine learning} powered packages such as \textbf{OpenCV}, \textbf{scikit-image}, and \textbf{PyTesseract} for use in robust error handling, decreasing errors by \textbf{94\%}, and increasing application efficiency by \textbf{49\%}.}
        \resumeItem{Performed efficient \textbf{data engineering}, reducing code complexity by \textbf{63\%}, and application runtime by \textbf{26\%}.}
        \resumeItem{Developed a \textbf{Java} desktop application for streamlined application usage, improving \textbf{UX} and portability by \textbf{100\%}.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\vspace*{-0.15in} % Adjust this value as needed
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
        {\textbf{\href{https://devpost.com/software/guitar-o3gw19}{GuitAR}} $|$ \emph{C\#, C++, Unity, Meta SDK, Algorithms, Audio Classification }}{June 2021 -- Present}
        \resumeItemListStart
          \resumeItem{\textbf{2nd place winner} of the "Best Overall" category at Knight Hacks 2024, surpassing \textbf{102} submitted projects.}
          \resumeItem{Developed a highly-interactive, educational mixed reality application for learning and practicing the guitar.}
          \resumeItem{Designed an \textbf{audio classification} algorithm which converts audio frequencies to binary data for note validation.}
          \resumeItem{Leveraged \textbf{C\#} to develop songs/lessons and core application logic, and utilized \textbf{Unity} for 3D development.}
        \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{\href{https://devpost.com/software/insurify-zj2dh4}{Insurify}} $|$ \emph{Python, Next.js, React, TypeScript, PostgreSQL, Prisma, Tailwind CSS, Docker, Flask}}{June 2021 -- Present}
          \resumeItemListStart
            \resumeItem{Built a multi-purpose insurance application which gives quotes based on a car's damage and customer data.}
            \resumeItem{Utilized \textbf{Python} and \textbf{Hugging Face Transformers} to develop an image classification model for car damage.}
            \resumeItem{Implemented a \textbf{machine learning} model for insurance quote estimation based on quantified car damage data.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://github.com/naavis-app/app}{Naavis}} $|$ \emph{Next.js, React, TypeScript, PostgreSQL, Prisma, Redis, Amazon Web Services, tRPC, Tailwind CSS, Jest}}{June 2021 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a location sharing web application which allows users to track locations of group members and devices.}
            \resumeItem{Implemented authentication with \textbf{TypeScript} and \textbf{AWS Cognito}, allowing third-party and regular sign-in.}
            \resumeItem{Used \textbf{Amazon S3}, \textbf{tRPC}, and \textbf{RESTful APIs} for assets, reducing query speed by \textbf{53\%}, and latency by \textbf{87\%}.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%

  %-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, TypeScript, R, C, C++, C\#, Java, Go, HTML, CSS, PowerShell, Bash, SQL} \\
     \textbf{Frameworks}{: React, Angular, Spring Boot, Next.js, Astro, Node.js, Express.js, Tailwind CSS, tRPC, Bootstrap} \\
     \textbf{Libraries}{: scikit-learn, PyTorch, TensorFlow, Keras, NumPy, Pandas, Matplotlib, Flask, Django, OpenCV} \\
     \textbf{Tools}{: Git, Jira, AWS, Microsoft Azure, Prisma, Redis, Docker, MongoDB, Jupyter Notebook, Linux} \\
    \textbf{Concepts}{: Machine Learning, Full-Stack Development, Computer Vision,
    Cloud Computing, DevOps, Agile/Scrum, Frontend, Backend, Data Science, Software Engineering} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
